---
title: "CS229_Project"
author: "John"
date: "November 15, 2017"
output: word_document
---

```{r DataModelTest}
write.csv(train, file = "trainInd.csv")
```

```{r DataRead}
#library(splines)
#library(leaps)
#library(gam)
#library(MASS)
#library(glmnet)
#library(tree)
#library(randomForest)

model.performance = function(a = y.test, b, bin =0) {
  
  if(bin == 0)
  {
    frchange.pred = (b-a)/a
    buy.decision = as.numeric(frchange.pred>0)
  }
  if(bin == 1)
  {
    buy.decision = b
  }
  correctbuy.decision = as.numeric(frac_change[-train]>0)
  #buy.decision
  daily.change = 1+(buy.decision * frac_change[-train])
  #print(length(daily.change))
  
  buy.days = daily.change
  #print("Model Performance - Buy decision based on prediction")
  mod.perf = prod(buy.days)
  cumROI = cumprod(buy.days)
  #print(mod.perf)
  #print("Baseline - Holding Bitcoin from day 1 of test set")
  base.perf = prod(1+frac_change[-train])
  #print(base.perf)
  return(list("Baseline"=base.perf, "Model"=mod.perf, "CumROI"=cumROI))
}



X = read.csv("C:/Users/John Martin/Downloads/MLProjectData1.csv", na.strings = "?", header = TRUE);
frac_change = X[,43]
x = as.data.frame(X[,2:42])

names(x) # x has 42 columns
# The last 2 columns are tmrws price and fractional change
y = X$Bitcoin.Price_tmrw
x = scale(x, center = TRUE, scale = TRUE);

set.seed(1)
train = sample(nrow(x),nrow(x)*0.7)
x.train = x[train,]
x.test = x[-train,]
y.train = y[train]
y.test = y[-train]


#plot(y, main ="Price of Bitcoin Jan 2011 - Dec 2013", xlab = "Day", ylab ="Price of Bitcoin (USD)")
```

```{r BagsnTreesnForests}
x = X[,2:42]
set.seed(1)
train = sample(nrow(x),nrow(x)*0.7)
y = X$Bitcoin.Price_tmrw
#x = as.data.frame(scale(x, center = TRUE, scale = TRUE));

x.train = x[train,]
x.test = x[-train,]
y.train = y[train]
y.test = y[-train]

tree.cs =tree(Bitcoin.Price_tmrw ~ ., data =x ,subset =train)

#Prediction
yhat = predict(tree.cs, newdata =x.test)

# Evaluation
a = x.test$up_down
b = yhat
result = model.performance(a,b)
print("Tree")
print(result$Model)

### Bagging
bag.cs =randomForest(Bitcoin.Price_tmrw~., data =x ,subset =train, mtry =10, importance =TRUE)

yhat = predict(bag.cs,newdata =x.test)
b = yhat
result = model.performance(a,b)
print("Bag")
print(result$Model)

importance(bag.cs)
varImpPlot (bag.cs)

```
```{r LassoRidge}

x = X[,2:42]
#names(x) # x has 42 columns
# The last 2 columns are tmrws price and fractional change
y = X$Bitcoin.Price_tmrw
#x = scale(x, center = TRUE, scale = TRUE);

set.seed(1)
train = sample(nrow(x),nrow(x)*0.7)
x.train = x[train,]
x.test = x[-train,]
y.train = y[train]
y.test = y[-train]

print("LASSO and Ridge")
cv.lasso = cv.glmnet(as.matrix(x.train[,1:40]),x.train$Bitcoin.Price_tmrw, alpha = 0)
bestlam = cv.lasso$lambda.min

lmb = 10^seq(-1,100,length = 100)
for (i in 1:100) {
  lasso.mod = glmnet(as.matrix(x.train[,1:40]),x.train$Bitcoin.Price_tmrw, alpha = 0, lambda = lmb[i])
  m0.pred = predict(lasso.mod, s = bestlam, newx =as.matrix(x.test[,1:40]))
  
  b = m0.pred
  a = x.test$Bitcoin.Price_tmrw
  result = model.performance(a,b)
  #print(lmb[i])
  #print(result$Model)
}

#Best LASSO
lasso.mod = glmnet(as.matrix(x.train[,1:40]),x.train$Bitcoin.Price_tmrw, alpha = 1, lambda = 98)
m0.pred = predict(lasso.mod, s = bestlam, newx =as.matrix(x.test[,1:40]))
b = m0.pred
a = x.test$Bitcoin.Price_tmrw
result = model.performance(a,b)
print("Best LASSO Model")
print(result$Model)

#Best Ridge Regression
ridge.mod = glmnet(as.matrix(x.train[,1:40]),x.train$Bitcoin.Price_tmrw, alpha = 0, lambda = 132194.1)
m0.pred = predict(ridge.mod, s = bestlam, newx =as.matrix(x.test[,1:40]))
b = m0.pred
a = x.test$Bitcoin.Price_tmrw
result = model.performance(a,b)
print("Best Ridge Regression")
print(result$Model)
ridge.mod$beta
```

```{r Logistic}

frac_change = X[,43]
x = X[,2:44]
#names(x) # x has 42 columns
# The last 2 columns are tmrws price and fractional change
y = X$Bitcoin.Price_tmrw
#x = as.data.frame(scale(x center = TRUE, scale = TRUE));

set.seed(1)
train = sample(nrow(x),nrow(x)*0.7)
x.train = x[train,]
x.test = x[-train,]
y.train = y[train]
y.test = y[-train]

# Logistic Regression

# Model
# Baseline Regression
#15x
#glm.fit = glm(up_down ~.-frac_change-Bitcoin.Price_tmrw, data =x, subset =train, family =binomial)
# Beat baseline

#50x
p_bct = 5 # 5,2
p_bctp = 2 # 2
p_ind = 1
p_pr = 4
p_r = 3
p_au = 3 # 3,4
p_lu = 1

#Best Model
glm.fit = glm(up_down ~ poly(CloseDJIA,p_ind) + poly(CloseSP500,p_ind) + poly(CloseStoxx600,p_ind) + poly(CloseBZF,p_ind) + 
                poly(bitcoin_trends,p_bct) + poly(bitcoinNews_trends,p_bct) + poly(bitcoinPrice_trends,p_bct) + 
                poly(bitcoin_trends_prev,p_bctp) + poly(bitcoinNews_trends_prev,p_bctp) + poly(bitcoinPrice_trends_prev,p_bctp) + 
                poly(Bitcoin.Price_prev,p_pr) + poly(Bitcoin.Price,p_pr) + 
                poly(signal_line,p_r) + poly(MACD,p_r) + 
                poly(active_users1,p_au) + poly(active_users2,p_au) + poly(active_users3,p_au) + poly(active_users4,p_au) + 
                poly(active_users1_prev,p_au) + poly(active_users2_prev,p_au) + poly(active_users3_prev,p_au) + poly(active_users4_prev,p_au) + 
                poly(lt_users1,p_lu) + poly(lt_users2,p_lu) + poly(lt_users3,p_lu) + poly(lt_users4,p_lu) + 
                poly(lt_users1_prev,p_lu) + poly(lt_users2_prev,p_lu) + poly(lt_users3_prev,p_lu) + poly(lt_users4_prev,p_lu)
              , data =x, subset =train, family =binomial)
# Train ROI
glm.pred = predict(glm.fit,x.train)
predDirection = (glm.pred>0)
table(predDirection,x.train$up_down)
a = x.train$up_down
b = as.numeric(predDirection)
result = model.performance(a,b,1)
print("Train ROI")
print(result$Model)
# Prediction
glm.pred = predict(glm.fit,x.test)
predDirection = (glm.pred>0)
table(predDirection,x.test$up_down)
# Evaluation
a = x.test$up_down
b = as.numeric(predDirection)
result = model.performance(a,b,1)
print("Test ROI")
print(result$Model)
plot(result$CumROI)
C1 = result$CumROI


#Without Search Trends
glm.fit = glm(up_down ~ poly(CloseDJIA,p_ind) + poly(CloseSP500,p_ind) + poly(CloseStoxx600,p_ind) + poly(CloseBZF,p_ind) + 
                poly(Bitcoin.Price_prev,p_pr) + poly(Bitcoin.Price,p_pr) + 
                poly(signal_line,p_r) + poly(MACD,p_r) + 
                poly(active_users1,p_au) + poly(active_users2,p_au) + poly(active_users3,p_au) + poly(active_users4,p_au) + 
                poly(active_users1_prev,p_au) + poly(active_users2_prev,p_au) + poly(active_users3_prev,p_au) + poly(active_users4_prev,p_au) + 
                poly(lt_users1,p_lu) + poly(lt_users2,p_lu) + poly(lt_users3,p_lu) + poly(lt_users4,p_lu) + 
                poly(lt_users1_prev,p_lu) + poly(lt_users2_prev,p_lu) + poly(lt_users3_prev,p_lu) + poly(lt_users4_prev,p_lu)
              , data =x, subset =train, family =binomial)
print("Without Search Trends")
# Prediction
glm.pred = predict(glm.fit,x.test)
predDirection = (glm.pred>0)
table(predDirection,x.test$up_down)
# Evaluation
a = x.test$up_down
b = as.numeric(predDirection)
result = model.performance(a,b,1)
print("Test ROI")
print(result$Model)
plot(result$CumROI)
C2 = result$CumROI


#Without Network Data
glm.fit = glm(up_down ~ poly(CloseDJIA,p_ind) + poly(CloseSP500,p_ind) + poly(CloseStoxx600,p_ind) + poly(CloseBZF,p_ind) + 
                poly(bitcoin_trends,p_bct) + poly(bitcoinNews_trends,p_bct) + poly(bitcoinPrice_trends,p_bct) + 
                poly(bitcoin_trends_prev,p_bctp) + poly(bitcoinNews_trends_prev,p_bctp) + poly(bitcoinPrice_trends_prev,p_bctp) + 
                poly(Bitcoin.Price_prev,p_pr) + poly(Bitcoin.Price,p_pr) + 
                poly(signal_line,p_r) + poly(MACD,p_r)
              , data =x, subset =train, family =binomial)
print("Without Network Data")
# Prediction
glm.pred = predict(glm.fit,x.test)
predDirection = (glm.pred>0)
table(predDirection,x.test$up_down)
# Evaluation
a = x.test$up_down
b = as.numeric(predDirection)
result = model.performance(a,b,1)
print("Test ROI")
print(result$Model)
plot(result$CumROI)
C3 = result$CumROI


#Without Both
glm.fit = glm(up_down ~ poly(CloseDJIA,p_ind) + poly(CloseSP500,p_ind) + poly(CloseStoxx600,p_ind) + poly(CloseBZF,p_ind) + 
                poly(Bitcoin.Price_prev,p_pr) + poly(Bitcoin.Price,p_pr) + 
                poly(signal_line,p_r) + poly(MACD,p_r)
              , data =x, subset =train, family =binomial)
print("Without Network Data & Search Trends")
# Prediction
glm.pred = predict(glm.fit,x.test)
predDirection = (glm.pred>0)
table(predDirection,x.test$up_down)
# Evaluation
a = x.test$up_down
b = as.numeric(predDirection)
result = model.performance(a,b,1)
print("Test ROI")
print(result$Model)
plot(result$CumROI)
C4 = result$CumROI

length(C1)
length(C2)
length(C3)
length(C4)
Cnames = c("Best Logistic Model","Without Search Trends","Without Network Data","Without Both")
write.table(cbind(C1,C2,C3,C4),row.names = FALSE , sep = ",", file ="CumulativeROIs.csv", col.names = Cnames)

```










```{r DataModeling}
#plot(y, main ="Price of Bitcoin Jan 2011 - Dec 2013", xlab = "Day", ylab ="Price of Bitcoin (USD)")


print("Model; Linear Regression with all predictors")
btc.m0 = lm(Bitcoin.Price~., data = x, subset = train)
summary(btc.m0)
#btc.m0$coefficients
m0.pred = predict(btc.m0, newdata =x.test)
mse = mean( ((m0.pred - y[-train])/y[-train])^2 )
mse
title = paste("Model 0: Linear Regression (All predictors) - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m0.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price",xlim =c(-100,1000), ylim =c(-100,1000))






print("Model; Linear Regression with all predictors")
btc.m0 = lm(frac_change ~ CloseDJIA + CloseDJIA_prev + CloseNikkei225 + bitcoin_trends + bitcoinPrice_trends + bitcoin_trends_prev + bitcoinPrice_trends_prev + bitcoinNews_trends + Bitcoin.Price_prev -frac_change - Bitcoin.Price, data = x.train)
#summary(btc.m0)
#btc.m0$coefficients
#btc.m0 = lm(frac_change ~ . - frac_change - Bitcoin.Price_tmrw, data = x.train)

m0.pred = predict(btc.m0, newdata =x.test)
#x.test$frac_change

a = m0.pred[x.test$frac_change!=0]
b = x.test$frac_change[x.test$frac_change!=0]
#a = a[-1]
#b = b[-1]

mse = mean( (a - b)^2 )
mse
title = paste("Model 0: Linear Regression (on fractional change) - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m0.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price")
# ,xlim =c(-100,1000), ylim =c(-100,1000)




print("Model; LASSO with all predictors")
cv.lasso = cv.glmnet(as.matrix(x.train[,1:40]),x.train$frac_change, alpha = 1)
bestlam = cv.lasso$lambda.min
lasso.mod = glmnet(as.matrix(x.train[,1:40]),x.train$frac_change, alpha = 1, lambda =bestlam)

m0.pred = predict(lasso.mod, s = bestlam, newx =as.matrix(x.test[,1:40]))
#x.test$frac_change

summary(lasso.mod)
lasso.mod$beta
a = m0.pred
b = x.test$frac_change

mse = mean( (a - b)^2 )
mse
title = paste("Lasso - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(x.test$frac_change,m0.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price")
# ,xlim =c(-100,1000), ylim =c(-100,1000)
```













```{r DataPlots}
par(mfrow=c(2,2)) 
plot(X$CloseDJIA,      X$Bitcoin.Price, main ="BTC Price vs. DJIA")
splinefit = smooth.spline(X$CloseDJIA, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfDJIA = splinefit$df

plot(X$CloseSP500,     X$Bitcoin.Price, main ="BTC Price vs. SP500")
splinefit = smooth.spline(X$CloseSP500, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfSP500 = splinefit$df

plot(X$CloseNikkei225, X$Bitcoin.Price, main ="BTC Price vs. Nikkie")
splinefit = smooth.spline(X$CloseNikkei225, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfNikkei225 = splinefit$df

plot(X$CloseStoxx600,  X$Bitcoin.Price, main ="BTC Price vs. Stoxx")
splinefit = smooth.spline(X$CloseStoxx600, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfStoxx600 = splinefit$df

plot(X$CloseBZF,       X$Bitcoin.Price, main ="BTC Price vs. BZF")
splinefit = smooth.spline(X$CloseBZF, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfBZF = splinefit$df

plot(X$CloseVIX,       X$Bitcoin.Price, main ="BTC Price vs. VIX")
splinefit = smooth.spline(X$CloseVIX, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfVIX = splinefit$df

plot(X$CloseCEW,       X$Bitcoin.Price, main ="BTC Price vs. CEW")
splinefit = smooth.spline(X$CloseCEW, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfCEW = splinefit$df

plot(X$active_users1,  X$Bitcoin.Price, main ="BTC Price vs. Active Users")
splinefit = smooth.spline(X$active_users1, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfAU = splinefit$df

plot(X$bitcoin_trends,  X$Bitcoin.Price, main ="BTC Price vs. bitcoin_trends")
splinefit = smooth.spline(X$bitcoin_trends, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfbt = splinefit$df

plot(X$bitcoinNews_trends,  X$Bitcoin.Price, main ="BTC Price vs. bitcoinNews_trends")
splinefit = smooth.spline(X$bitcoinNews_trends, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfbnt = splinefit$df

plot(X$bitcoinPrice_trends,  X$Bitcoin.Price, main ="BTC Price vs. bitcoinPrice_trends")
splinefit = smooth.spline(X$bitcoinPrice_trends, X$Bitcoin.Price, cv = TRUE)
lines(splinefit,col ="red")
dfbpt = splinefit$df

```

```{r LottaRegression}
library(splines)
library(leaps)
library(gam)

set.seed(1)
train = sample(nrow(x),nrow(x)*0.7)
x.train = x[train,]
x.test = x[-train,]


print("Model 0; Linear Regression with all predictors")
btc.m0 = lm(Bitcoin.Price~., data = x, subset = train)
summary(btc.m0)
#btc.m0$coefficients
m0.pred = predict(btc.m0, newdata =x.test)
model.performance(y[-train],m0.pred)$Model
title = paste("Model 0: Linear Regression (All predictors) - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m0.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price",xlim =c(-100,1000), ylim =c(-100,1000))

par(mfrow=c(2,2))

print("Model 1; Linear Regression (All except ActiveUsers) - Test MSE: ")
btc.m1 = lm(Bitcoin.Price~.-active_users1, data = x, subset = train)
#btc.m1$coefficients
m1.pred = predict(btc.m1, newdata =x.test)
model.performance(y[-train],m1.pred)$Model
title = paste("M1 All (-ActiveUsers) - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m1.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,1000), ylim =c(-100,1000))

print("Model 2; Linear Regression with 3 predictors : Search Trends")
btc.m2 = lm(Bitcoin.Price~ bitcoin_trends + bitcoinNews_trends + bitcoinPrice_trends , data = x, subset = train)
#btc.m2$coefficients
m2.pred = predict(btc.m2, newdata =x.test)
model.performance(y[-train],m2.pred)$Model
title = paste("M2 3 Predictors:Trends - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m2.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,1000), ylim =c(-100,1000))

print("Model 3; Linear Regression with 5 predictors: Stock Market and Currency Indices")
btc.m3 = lm(Bitcoin.Price~ CloseDJIA + CloseSP500 + CloseBZF + CloseCEW + CloseStoxx600, data = x, subset = train)
#btc.m3$coefficients
m3.pred = predict(btc.m3, newdata =x.test)
model.performance(y[-train],m3.pred)$Model
title = paste("M3 Predictors:Indices - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m3.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,1000), ylim =c(-100,1000))

print("Model 4; Linear Regression with polynomial predictors (degree 3) - No Search Trends")
btc.m4 = lm(Bitcoin.Price~ poly(CloseDJIA,3) + poly(CloseSP500,3) + poly(CloseNikkei225,3) + poly(CloseBZF,3) + poly(CloseVIX,3) + poly(CloseCEW,3), data = x, subset = train)
#btc.m4$coefficients
m4.pred = predict(btc.m4, newdata =x.test)
model.performance(y[-train],m4.pred)$Model
title = paste("M4 Poly(3):Indices - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m4.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,1000), ylim =c(-100,1000))


print("Model 5; Linear Regression with polynomial predictors (degree 4) - No Search Trends")
btc.m5 = lm(Bitcoin.Price~ poly(CloseDJIA,4) + poly(CloseSP500,4) + poly(CloseNikkei225,4) + poly(CloseBZF,4) + poly(CloseVIX,4) + poly(CloseCEW,4) + poly(active_users1,5), data = x, subset = train)
#btc.m5$coefficients
m5.pred = predict(btc.m5, newdata =x.test)
model.performance(y[-train],m5.pred)$Model
title = paste("M5 Poly(4) no Trends - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m5.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,1000), ylim =c(-100,1000))

print("Model 6; Linear Regression - Search Trends (Bitcoin) - Test MSE:  ")
btc.m6 = lm(Bitcoin.Price~ bitcoin_trends, data = x, subset = train)
#btc.m6$coefficients
m6.pred = predict(btc.m6, newdata =x.test)
model.performance(y[-train],m6.pred)$Model
title = paste("M6 Trends (Bitcoin) - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m6.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,1000), ylim =c(-100,1000))

print("Model 7; Linear Regression - Search Trends (BitcoinNews) - Test MSE:  ")
btc.m7 = lm(Bitcoin.Price~ bitcoinNews_trends, data = x, subset = train)
#btc.m7$coefficients
m7.pred = predict(btc.m7, newdata =x.test)
model.performance(y[-train],m7.pred)$Model
title = paste("M7 Trends (BTCNews) - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m7.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,1000), ylim =c(-100,1000))

print("Model 8; Linear Regression - Search Trends (BitcoinPrice) - Test MSE:  ")
btc.m8 = lm(Bitcoin.Price~ bitcoinPrice_trends, data = x, subset = train)
#btc.m8$coefficients
m8.pred = predict(btc.m8, newdata =x.test)
model.performance(y[-train],m8.pred)$Model
title = paste("M8 Trends (BTCPrice) - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(y[-train],m8.pred,main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,1000), ylim =c(-100,1000))

```


```{r Best Linear Model}
print("Model Test; Linear Regression with polynomial predictors (degree 4)")
#btc.mt = lm(Bitcoin.Price~ bitcoinNews_trends, data = x, subset = train)

x = X[,2:42]
set.seed(1)
train = sample(nrow(x),nrow(x)*0.7)
y = X$Bitcoin.Price_tmrw
#x = as.data.frame(scale(x, center = TRUE, scale = TRUE));

x.train = x[train,]
x.test = x[-train,]
y.train = y[train]
y.test = y[-train]

# Model
btc.mt = lm(Bitcoin.Price~ poly(bitcoin_trends,3) + poly(bitcoinNews_trends,3) + poly(bitcoinPrice_trends,3) + poly(CloseDJIA,4) + poly(CloseSP500,4) + poly(CloseNikkei225,4) + poly(CloseBZF,4) + poly(CloseVIX,4) + poly(CloseCEW,4) + poly(active_users1,5), data = x, subset = train)
#btc.mt$coefficients

# Prediction
mt.pred = predict(btc.mt, newdata =x.test)
title = paste("M9 Polynomial Predictors (degrees 3 - 5) - Test MSE:",format(mse,digits = 5,nsmall = 2), sep = " ")
plot(ytest[mt.pred<500],mt.pred[mt.pred<500],main =title, xlab ="Price from Test Data", ylab ="Predicted Price", xlim =c(-100,400), ylim =c(-100,400))

# Evaluation
a = y.test
b = mt.pred
model.performance(a,b)

```


# Expt
p_bct = 5
p_bctp = 2
p_ind = 1
p_pr = 4
p_r = 3
p_au = 3
p_lu = 1
p_int = 1

for (i in 1:6) {
  p_bct = i
  print(i)
  glm.fit = glm(up_down ~ poly(CloseDJIA,p_ind) + poly(CloseSP500,p_ind) + poly(CloseStoxx600,p_ind) + poly(CloseBZF,p_ind) +
                poly(bitcoin_trends,p_bct) + poly(bitcoinNews_trends,p_bct) + poly(bitcoinPrice_trends,p_bct) +
                poly(bitcoin_trends_prev,p_bctp) + poly(bitcoinNews_trends_prev,p_bctp) + poly(bitcoinPrice_trends_prev,p_bctp) +
                poly(Bitcoin.Price_prev,p_pr) + poly(Bitcoin.Price,p_pr) + 
                poly(signal_line,p_r) + poly(MACD,p_r) +
                poly(active_users1,p_au) + poly(active_users2,p_au) + poly(active_users3,p_au) + poly(active_users4,p_au) +
                poly(active_users1_prev,p_au) + poly(active_users2_prev,p_au) + poly(active_users3_prev,p_au) + poly(active_users4_prev,p_au) +
                poly(lt_users1,p_lu) + poly(lt_users2,p_lu) + poly(lt_users3,p_lu) + poly(lt_users4,p_lu) +
                poly(lt_users1_prev,p_lu) + poly(lt_users2_prev,p_lu) + poly(lt_users3_prev,p_lu) + poly(lt_users4_prev,p_lu)
              , data =x, subset =train, family =binomial)
          
# Prediction
glm.pred = predict(glm.fit,x.test)
predDirection = (glm.pred>0)
table(predDirection,x.test$up_down)

# Evaluation
a = x.test$up_down
b = as.numeric(predDirection)
result = model.performance(a,b,1)
print(result$Model)

}

